### 2023-04-29 main/chapter_experiment.tex
incorporate Karolos's suggestions; format bib

% luminosity and its uncertainty
The luminosity delivered to each detector varies with its local beam controls.
For example, beams at the \lhcb\ and \alice\ interaction points are
deliberately offset to reduce data rates and `pile-up' backgrounds from
multiple interactions~\cite{Follin:2014nva}
The peak instantaneous luminosity delivered by the LHC to \atlas\ in Run~2 was
$1.9\times10^{34}\,\mathrm{cm}^{-2}\mathrm{s}^{-1}$ in 2018;
see Table~\ref{tab:experiment_run2_state} for more details here.
% Van Der Meer scans
Luminosity is measured in \atlas\ during dedicated low-luminosity runs of the
LHC, using the ``van der Meer'' method, which measures interaction rates while
scanning the beams across each other in transverse
space~\cite{vanderMeer:296752,ATLAS:2022hro}.
These \atlas\ luminosity measurements primarily rely on data from the
LUCID2 Cherenkov detector, which comprises two parts that are offset from the
interaction point by about $\pm 17\,\mathrm{m}$ along the beam-pipe~\cite{
SBARRA2019152,
Avoni_2018
}.
The relative uncertainty on \atlas's Run~2 integrated luminosity is
$\pm1.7\%$~\cite{atlas2022searches}.

>>>>

% luminosity and its uncertainty
The luminosity delivered to each detector varies with its local beam controls.
For example, beams at the \lhcb\ and \alice\ interaction points are
deliberately offset to reduce data rates and `pile-up' backgrounds from
multiple interactions~\cite{Follin:2014nva}
The peak instantaneous luminosity delivered by the LHC to \atlas\ in Run~2 was
$1.9\times10^{34}\,\mathrm{cm}^{-2}\mathrm{s}^{-1}$ in 2018;
see Table~\ref{tab:experiment_run2_state} for more details here.
% Van Der Meer scans
Luminosity is measured in \atlas\ during dedicated low-luminosity runs of the
LHC, using the ``van der Meer'' method, which measures interaction rates while
scanning the beams across each other in transverse
space~\cite{vanderMeer:296752,ATLAS:2022hro}.
These \atlas\ luminosity measurements primarily rely on data from the
LUCID2 Cherenkov detector, which comprises two parts that are offset from the
interaction point by about $\pm 17\,\mathrm{m}$ along the beam-pipe~\cite{
SBARRA2019152,
Avoni_2018
}.
The relative uncertainty on \atlas's Run~2 integrated luminosity,
in the form that we use in the $\twoljets$ search,
is $\pm1.7\%$~\cite{atlas2022searches,ATLAS-CONF-2019-021}.
More recent measurements have reduced this uncertainty to
$\pm0.83\%$~\cite{ATLAS:2022hro}.
